\sysfull

### 2018-04-16 paper/newCoalescing.tex
update the ea algo

The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy, having the target budget $B$ to increase by $x$ static tasks after a successful completion of a coalesced task, and to decrease by the same number of tasks upon a reboot. In this case: 
\begin{itemize}
\item $f_\text{reboot}(B) = B - x $;
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{coalesc\_task\_maker}(B) = B + x$; 
\end{itemize}
Since this algorithm relies on an \em{energy blind counting process} that enlarges the coalesced task size by $x$ static tasks on a successful completion, and reduces its size by $x$ on a reboot. this algorithm is slow in reacting to the changes in energy conditions; the energy required by a coalesced task or the available energy. In particular, this algorithm can experience a large number of \emph{repeated power} failures without forward progress, (see figure~\ref{fig:energyBlind}). In other words, if a coalesced task size is enlarged ten times, due to ample amount of energy or coalescing small static tasks, and then the algorithm can only progress by a single static task, due to a change in energy condition, the devise has to reboot for ten times to have an adequate coalesced task size. Moreover, This algorithm tend to experience a large re-execution penalty due to its unawareness of the energy conditions and it optimistic behavior.

>>>>

The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy, having the target budget $B$ to increase by $x$ static tasks after a successful completion of a coalesced task, and to decrease by the same number of tasks upon a reboot. In this case: 
\begin{itemize}
\item $f_\text{reboot}(B) = B - x $;
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{coalesc\_task\_maker}(B) = B + x$; 
\end{itemize}
Since this algorithm relies on an \emph{energy blind counting process} that enlarges the coalesced task size by $x$ static tasks on a successful completion, and reduces its size by $x$ on a reboot. this algorithm is slow in reacting to the changes in energy conditions; the energy required by a coalesced task or the available energy. In particular, this algorithm can experience a large number of \emph{repeated power} failures without forward progress, (see figure~\ref{fig:energyBlind}). In other words, if a coalesced task size is enlarged ten times, due to ample amount of energy or coalescing small static tasks, and then the algorithm can only progress by a single static task, due to a change in energy condition, the devise has to reboot for ten times to have an adequate coalesced task size. Moreover, This algorithm tend to experience a large re-execution penalty due to its unawareness of the energy conditions and it optimistic behavior.
